Reionization Planck 2018 Notes

### 2021-01-07 results/notes.tex

>>>>

\begin{figure}
%
\includegraphics[width=0.35\textwidth]{results/cosmomc_kde/pl18_tanh_highz_test5_run1_vs_relike_tanh_highz_test9_run1_f0p28_taulo_prior_0p03_zre_prior_6p1_taulo_prior_0p0_tri_smooth_scale_1D_0.3_num_bins_1D_100_smooth_scale_2D_0.3_num_bins_2D_100.png}
\includegraphics[width=0.35\textwidth]{results/cosmomc_kde/pl18_tanh_highz_test5_run1_vs_relike_tanh_highz_test9_run1_f0p28_taulo_prior_0p03_zre_prior_6p1_taulo_prior_0p0_tri_smooth_scale_1D_0.5_num_bins_1D_100_smooth_scale_2D_0.5_num_bins_2D_100.png}
%
\includegraphics[width=0.35\textwidth]{results/cosmomc_kde/pl18_tanh_highz_test5_run1_vs_relike_tanh_highz_test9_run4_f0p18_taulo_prior_0p03_zre_prior_6p1_taulo_prior_0p0_tri_smooth_scale_1D_0.3_num_bins_1D_100_smooth_scale_2D_0.3_num_bins_2D_100.png}
\includegraphics[width=0.35\textwidth]{results/cosmomc_kde/pl18_tanh_highz_test5_run1_vs_relike_tanh_highz_test9_run4_f0p18_taulo_prior_0p03_zre_prior_6p1_taulo_prior_0p0_tri_smooth_scale_1D_0.5_num_bins_1D_100_smooth_scale_2D_0.5_num_bins_2D_100.png}
%
\includegraphics[width=0.35\textwidth]{results/cosmomc_kde/pl18_tanh_highz_test5_run1_vs_relike_tanh_highz_test8_run9_f0p14_taulo_prior_0p03_zre_prior_6p1_taulo_prior_0p0_tri_smooth_scale_1D_0.3_num_bins_1D_100_smooth_scale_2D_0.3_num_bins_2D_100.png}
\includegraphics[width=0.35\textwidth]{results/cosmomc_kde/pl18_tanh_highz_test5_run1_vs_relike_tanh_highz_test8_run9_f0p14_taulo_prior_0p03_zre_prior_6p1_taulo_prior_0p0_tri_smooth_scale_1D_0.5_num_bins_1D_100_smooth_scale_2D_0.5_num_bins_2D_100.png}
%
\includegraphics[width=0.35\textwidth]{results/cosmomc_kde/pl18_tanh_highz_test5_run1_vs_relike_tanh_highz_test9_run3_f0p10_taulo_prior_0p03_zre_prior_6p1_taulo_prior_0p0_tri_smooth_scale_1D_0.3_num_bins_1D_100_smooth_scale_2D_0.3_num_bins_2D_100.png}
\includegraphics[width=0.35\textwidth]{results/cosmomc_kde/pl18_tanh_highz_test5_run1_vs_relike_tanh_highz_test9_run3_f0p10_taulo_prior_0p03_zre_prior_6p1_taulo_prior_0p0_tri_smooth_scale_1D_0.5_num_bins_1D_100_smooth_scale_2D_0.5_num_bins_2D_100.png}
%
\label{fig:}
\caption{Left: getdist smooth\_scale\_1D = smooth\_scale\_2D = 0.3; Right: same as left but with 0.5.
} 
\end{figure}
